Modern Graph Generators: A Survey

### 2018-11-07 generators_SocialNetworks.tex
iThenticate modifications - part II

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
realistic social networks using a combination of public and private data sets
and large-scale agent based techniques. The process works as follows: In the first step
it creates a synthetic population by integrating databases from commercial and
public sources. In the second step, a set of activity templates are determined. Each
synthetic individual is assigned a 24-hour activity sequence including
geolocations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
United States that models every individual in the population. The synthetic
population is a set of geographically located people and households. Household
structure and demographics are derived from U.S. Census data. The activity
templates are  based on several thousand responses to an activity or time-use
survey. Demographic information for each person and location, a minute-by-minute
schedule of each person's activities, and the locations where these activities
take place is generated by a combination of simulation and data fusion
techniques. This information is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.

\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
types of social network graphs -- the \emph{linkage graph}, where nodes stand
for the people in the social network and edges are their friendship links, and
the \emph{activity graph}, where nodes also stand for the people but edges stand
for their interactions. On the basis of the analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
the authors discover that they both exhibit power-law degree distribution, high
clustering coefficient (community structure), and small diameter; also regarding
the dynamic properties they both follow the densification law and have relatively stable
clustering coefficient over time. However, the authors do not observe diameter
shrinking in opinions activity graph and there is a difference in degree
correlation (how frequently nodes with similar degrees connect to each other).
Namely linkage graphs have positive degree correlation whereas activity graphs
show neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs
with positive degree correlation. For this purpose it extends the forest
fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
which is in charge of the burning process, and the \emph{symmetry probability}
$P_s$ which indicates backward linking from old nodes to new ones. $P_b$
controls a BFS-based forward burning process. The fire burns increasingly
fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it
brings more links. It gives chances for big nodes to connect back to big nodes.

\paragraph{LinkBench} The LinkBench
benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed to predict the
performance of a database when used for persistent storage of Facebook's
production data. The benchmark considers true Big Data and related problems with
sharding, replication etc. The social graph at Facebook comprises objects (nodes
with IDs, version, timestamp and data) and associations (directed edges, pairs
of node IDs, with visibility, timestamp and data). The size of the target graph
is the number of nodes. Graph edges are generated concurrently with graph nodes
during bulk loading. The node ID space is divided into chunks based on the ID of
the source node which  are processed in parallel. The edges of the graph are
generated in accordance with the results of analysing  real-world Facebook data
(such as outdegree distribution). A workload corresponding to 10 graph
operations (such as insert object, count the number of associations etc.) and
their respective characteristics over the real-world data is generated for the
synthetic data.

>>>>

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
realistic social networks. For this purpose the authors combine both public and private data sets
with large-scale agent based techniques. The process works as follows: In the first step
it creates a synthetic population by integrating public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
geolocations is assigned to each synthetic individual. To demonstrate the approach, the authors create a synthetic US population consisting of people and households together with respective geolocations. For this purpose the authors combine simulation and data fusion techniques utilizing various real-world data sources such as U.S. Census data, responses to an activity survey or a time-use survey. %Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
The result is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.

\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
types of social network graphs -- the \emph{linkage graph}, where nodes represent people and edges correspond to their friendships, and the \emph{activity graph}, where nodes also represent people but correspond to their interactions. On the basis of the analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit high clustering coefficient (community structure), small diameter, and power-law degree distribution. Considering the dynamic properties they both have relatively stable clustering coefficient over time and follow the densification law. On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive, activity graphs neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation. For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
link symmetry. It has two parameters the \emph{burning probability} $P_b$ and \emph{symmetry probability} $P_s$. $P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking from old nodes to new nodes and ``adds fuel to the fire as it brings more links''. %It gives chances for big nodes to connect back to big nodes.

\paragraph{LinkBench} The LinkBench
benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed for the purpose of analysis of efficiency of a database storing Facebook's production data. The benchmark considers true Big Data and related problems with sharding, replication etc. The social graph at Facebook comprises objects (nodes with IDs, version, timestamp and data) and associations (directed edges, pairs of node IDs, with visibility, timestamp and data). The size of the target graph is the number of nodes. Graph edges and nodes are generated concurrently during bulk loading. The space of node IDs is divided into chunks which enable parallel processing. The edges of the graph are generated in accordance with the results of analysing  real-world Facebook data (such as outdegree distribution). A workload corresponding to 10 graph operations (such as insert object, count the number of associations etc.) and their respective characteristics over the real-world data is generated for the synthetic data.
